Rusty Linux: Advances in Rust for Linux Kernel Development

### 2024-10-24 slides.tex
updated proofs dir

\begin{frame}
  \frametitle{Our Research}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      We aim to find the current advances in using Rust in Kernel development to reduce the number of
      memory safety vulnerabilities in one of the most critical pieces of software that underpins all
      modern applications.
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{figure}
        \caption{A rusty computer\footnotemark[1]}
        \includegraphics[width=.8\textwidth]{images/rusty.jpeg}\footnotemark[1]
      \end{figure}
    \end{column}
  \end{columns}
  \footnotetext[1]{AI Prompt: A rusty computer with a penguin next to it}
  \href{https://github.com/shanep/esem-2024/blob/master/proofs/esem24-50.pdf}{\beamergotobutton{Paper
    Link}}
\end{frame}

@@

\begin{frame}
  \frametitle{RQ4: Lessons Learned}
  \begin{itemize}
  \item<1-> Impossible to use 100$\%$ rust
  \item<2-> Rust is not as expressive as other formal verification techniques
  \item<3-> Ownership root - An OS provides memory to rust so if the OS is itself written in rust
    who is the root owner?
    \begin{itemize}
      \item Research is needed for hardware support (CHERI)
  \end{itemize}

>>>>

\begin{frame}
  \frametitle{Our Research}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      We aim to find the current advances in using Rust in Kernel development to reduce the number of
      memory safety vulnerabilities in one of the most critical pieces of software that underpins all
      modern applications (SLR).
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{figure}
        \caption{A rusty computer\footnotemark[1]}
        \includegraphics[width=.8\textwidth]{images/rusty.jpeg}\footnotemark[1]
      \end{figure}
    \end{column}
  \end{columns}
  \footnotetext[1]{AI Prompt: A rusty computer with a penguin next to it}
  \href{https://github.com/shanep/esem-2024/blob/master/proofs/esem24-50.pdf}{\beamergotobutton{Paper
    Link}}
\end{frame}

@@

\begin{frame}
  \frametitle{RQ4: Lessons Learned}
  \begin{itemize}
  \item<1-> Impossible to use 100$\%$ rust
  \item<2-> Rust is not as expressive as other formal verification techniques
  \item<3-> Ownership root - An OS provides memory to rust so if the OS is itself written in rust
    who is the root owner?
    \begin{itemize}
    \item Open research question if this can even be done in software
    \item Researchers looking at hardware support (CHERI)
    \end{itemize}
  \end{itemize}
